\chapter{Output Directory}
\hypertarget{output-directory}{}

Each of the major functions is able to create image feedback to verify
that the software is functioning properly. The image files are written
to a directory, so they can be shared between different parts of the
application. For this reason, there always needs to be an output
directory that the software can write to.

This output directory also serves as the starting point when choosing
to save some text or images to a new file.

\begin{itemize}

\item You can set the output directory in the configuration file, on
  the command line, or using the GUI.

\item If you are working on a project that involves assembling a large
  collection of images or text, you may wish to set the output
  directory to a special folder for that project.

\item You can set the output directory to a temp directory that is
  emptied every day, if that is something you think about.

\end{itemize}

\section{Output Directory Files}

A sample output directory has been created for you, so that the
software will function right out of the box. That sample directory was
created right in the root folder:

\begin{verbatim}
    catamount/output/
\end{verbatim}

\section{Output Directory Settings}

The path to the output directory is a ``global setting'' because all
of the different major functions need some disk space to write to, in
order to do their job. The output directory can be set on the command
line, or from the GUI.

Output directory settings are expected in the following format:

\begin{description}

\item[outdir\_path PATH]
\hypertarget{global-outdir-path}{}

Select an output directory where the software can make some files, and
that serves as the base directory for ``Save As'' operations.
\verb=PATH= should be a path to a directory, like \verb=C:\jane\stuff\output=.

The argument is of type \hyperlink{argument-type-path}{PATH}

\end{description}


\section{Output Directory @ Configuration File}

The output directory is represented in the configuration file by the
following option:

\begin{verbatim}
    [Global_Settings]
    outdir_path = C:\path\to\catamount\output
\end{verbatim}

Change that setting to a full path where the software can write out
images.
