\chapter{Install CatAmount On Mac OS X}
\hypertarget{macosx-install-catamount}{}

\section{Before You Start}
\hypertarget{setup}{}

Before getting into the setup of the application, make sure Python 3
is installed, along with necessary shared libraries. Refer to the
following sections:

\begin{itemize}
\item \hyperlink{macosx-install-python}{Install Python On Mac OS X}
\item \hyperlink{macosx-install-libraries}{Install Libraries On Mac OS X}
\end{itemize}

\section{Setup Procedure}

CatAmount is just a zip archive with files in it. You should unzip
the files into a directory where it can live, and where you will
remember it lives. For a simple example, we will place the software
on the desktop.

\begin{verbatim}
    /Users/joe/Desktop/catamount/
\end{verbatim}

Choose a directory, and unzip the zip archive. When you are done,
you should wind up with approximately the following set of files.
I'm including notes about what each file does.

\begin{verbatim}
    catamount/                     <== CatAmount home
    catamount/data/
    catamount/data/ALLGPS.csv      <== Sample data file
    catamount/data/survey_file.csv <== Sample survey data file
    catamount/fonts/
    catamount/fonts/proggy.pbm     <== Fonts used by image tools
    catamount/fonts/proggy.pil     <== Fonts used by image tools
    catamount/output/              <== Default output directory
    catamount/catamount.conf       <== Configuration file
    catamount/find_clusters.py     <== CLI program to find clusters
    catamount/find_crossings.py    <== CLI program to find crossings
    catamount/find_whodunit.py     <== CLI program to find whodunit
    catamount/match_survey_to_cluster.py
                                   \== CLI program to match surveys to clusters
    catamount/show_territories.py  <== CLI program to show territories
    catamount/tkcatamount.pyw      <== GUI
    catamount/catamount/*          <== Python "project" for shared code
\end{verbatim}

\section{Make Sure It Works}

If the prerequisites are in place, and the files are in place, then things
should work. To test it, open up a terminal window (\texttt{Applications > Utilities > Terminal.app}).

In the terminal window, change directories until you are in the CatAmount
folder.

\begin{verbatim}
    cd /Users/joe/Desktop/catamount/
\end{verbatim}

Try to run one of the command-line programs:

\begin{verbatim}
    $ ./find_clusters.py --help
\end{verbatim}

If that gives you helpful messages, then everything is okay. If it complains
that something is missing, there is more work to do.

At this point you can also try launching the GUI.

\begin{verbatim}
    $ ./tkcatamount.pyw
\end{verbatim}

If the GUI doesn't launch and doesn't give any error messages, try launching
it as an argument to the Python interpreter:

\begin{verbatim}
    $ python3 tkcatamount.pyw
\end{verbatim}

If you run into persistent problems launching the applications, the best way
to get help is to email me the error messages. If you don't have my email address
you can contact me via \url{http://www.kasploosh.com/}.
